Cheminformatics: The Computer Science of Chemical Discovery

### 2011-07-13 paper.tex

\category{H.4}{Information Systems Applications}{Miscellaneous}
\terms{
\begin{itemize}
\item \textit{Tautomerism} - Tautomers are isomers (same molecular formula but different structural formula) of organic compounds that readily interconvert by a chemical reaction called tautomerization.
\item \textit{Protonation and protonation state} - In chemistry, protonation is the addition of a proton (H+) to an atom, molecule, or ion. The different states (different number of H+ or on different atoms) are called protonation states for a molecular compound (e.g. de-protonated, mono-protonated, bi-protonated, or any variations of those states).
\item \textit{BioAssay} - A system measuring the biological activity of a chemical compound on a particular biological assay (with all its parameters).
\item \textit{Metabolites} - Metabolites are the intermediates and products of metabolism. The term metabolite is usually restricted to small molecules (chemical compounds).
\item \textit{Mass spectrometry} - Mass spectrometry (MS) is an analytical technique that measures the mass-to-charge ratio of charged particles. It is used for determining masses of particles, for determining the elemental composition of a sample or molecule, and for elucidating the chemical structures of molecules, such as peptides and other chemical compounds.
\item \textit{Ligand (coordination chemistry)} - an atom, ion, or functional group that donates one or more of its electrons through a coordinate covalent bond to one or more central atoms or ions
\item \textit{Ligand (biochemistry)} - a substance that binds to a protein
\item \textit{Receptor (biochemistry)} - in biochemistry, a protein molecule that receives and responds to a neurotransmitter, or other substance
\item \textit{Proteochemometric modeling} - combining data mining for chemical compounds (ligands) and proteins within the same machine learning framework 
\item \textit{BioDegradation} - is the chemical dissolution of materials by bacteria or other biological means.
\item \textit{Reaction catalyses} - Catalysis is the change in rate of a chemical reaction due to the participation of a substance called a catalyst.
\item \textit{Conformation and conformational isomerism} - In chemistry, conformational isomerism is a form of stereoisomerism in which the isomers can be interconverted exclusively by rotations about formally single bonds. Single possible states of compounds are called conformers.
\item \textit{SMARTS} - SMiles ARbitrary Target Specification is a language for specifying substructural patterns. in molecules
\end{itemize}
}
\keywords{cheminformatics, graphs, chemistry, databases, knowledge management, open source, open data}

>>>>

\category{H.4}{Information Systems Applications}{Miscellaneous}
\terms{
\begin{itemize}
\item \textit{Tautomerism} - Tautomers are isomers (same molecular formula but different structural formula) of organic compounds that readily interconvert by a chemical reaction called tautomerization.
\item \textit{Protonation and protonation state} - In chemistry, protonation is the addition of a proton (H$^+$) to an atom, molecule, or ion. The different states (different number of H$^+$ or on different atoms) are called protonation states for a molecular compound (e.g. de-protonated, mono-protonated, bi-protonated, or any variations of those states).
\item \textit{BioAssay} - A system measuring the biological activity of a chemical compound on a particular biological assay (with all its parameters).
\item \textit{Metabolites} - Metabolites are the intermediates and products of metabolism. The term metabolite is usually restricted to small molecules (chemical compounds).
\item \textit{Mass spectrometry} - Mass spectrometry (MS) is an analytical technique that measures the mass-to-charge ratio of charged particles. It is used for determining masses of particles, for determining the elemental composition of a sample or molecule, and for elucidating the chemical structures of molecules, such as peptides and other chemical compounds.
\item \textit{Ligand (coordination chemistry)} - an atom, ion, or functional group that donates one or more of its electrons through a coordinate covalent bond to one or more central atoms or ions
\item \textit{Ligand (biochemistry)} - a substance that binds to a protein
\item \textit{Receptor (biochemistry)} - in biochemistry, a protein molecule that receives and responds to a neurotransmitter, or other substance
\item \textit{Proteochemometric modeling} - combining data mining for chemical compounds (ligands) and proteins within the same machine learning framework 
\item \textit{BioDegradation} - is the chemical dissolution of materials by bacteria or other biological means.
\item \textit{Reaction catalyses} - Catalysis is the change in rate of a chemical reaction due to the participation of a substance called a catalyst.
\item \textit{Conformation and conformational isomerism} - In chemistry, conformational isomerism is a form of stereoisomerism in which the isomers can be interconverted exclusively by rotations about formally single bonds. Single possible states of compounds are called conformers.
\item \textit{SMARTS} - SMiles ARbitrary Target Specification (SMARTS) is a language for specifying substructural patterns in molecules
\end{itemize}
}
\keywords{cheminformatics, graphs, chemistry, databases, knowledge management, open source, open data}
